---
title: "unfiltered_Depmap_heatmap"
author: "Shaun"
date: "2024-01-16"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load packages, include=FALSE}
library(ComplexHeatmap)
library(PharmacoGx)
library(magicaxis)
library(dplyr)

#if (!requireNamespace('BiocManager', quietly = TRUE))
#  install.packages('BiocManager')
#BiocManager::install('ComplexHeatmap')
#BiocManager::install('PharmacoGx')

pkgs <- c("tidyverse", "reshape2", "magrittr", "circlize", "plotly", "gghighlight", "ggrepel", "drc", "ggpubr", "viridis")

check <- sapply(pkgs, require, warn.conflicts = TRUE, character.only = TRUE)
if(any(!check)){
  pkgs.missing <- pkgs[!check]
  install.packages(pkgs.missing)
  check <- sapply(pkgs.missing, require, warn.conflicts = TRUE, character.only = TRUE)
}
#if (!requireNamespace('BiocManager', quietly = TRUE))
#  install.packages('BiocManager')
#BiocManager::install('ComplexHeatmap')
#BiocManager::install('PharmacoGx')


```


## T-test and Anova testing

This code performs t-tests and ANOVA tests for each gene, creates visualizations of the "Chronos" scores across different lineages


Read data

```{r read_data_crispr}
crispr <- read.delim(file = "~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/metadata/CRISPR_(DepMap_Public_23Q4+Score,_Chronos)_subsetted.csv", header = TRUE, sep = ",", check.names = FALSE, stringsAsFactors = FALSE) # read in data
crispr <- crispr[, -c(1, 4, 5, 6, 7, 8)] # get rid of unneeded columns 
#crispr <- crispr[,!apply(is.na(crispr), 2, any)] # removes columns from the "crispr" data frame that contain any missing values.
```



```{r, include=FALSE, eval=FALSE}
NIH_E3_list <- read_excel(path = "~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/Definite_Ligase_List.xlsx")
```


```{r, include=FALSE, eval=FALSE}
not_in_crispr_in_E3_list <- NIH_E3_list$`Gene Symbol`[!(toupper(NIH_E3_list$`Gene Symbol`) %in% crispr_colnames)]
already_not_in_crispr <- c("MARCH1", "MARCH10", "MARCH11", "MARCH2", "MARCH3", "MARCH4", "MARCH5", "MARCH6", "MARCH7", "MARCH8", "MARCH9", "PARK2", "RFWD2", "RNF219", "ZNF645")
#not_in_crispr[!(not_in_crispr %in% crispr_colnames)]

not_in_crispr_not_the_15 <- not_in_crispr[!(not_in_crispr %in% already_not_in_crispr)]

not_in_crispr_not_the_15[!(not_in_crispr_not_the_15 %in% colnames(crispr)[3:length(colnames(crispr))])]

in_E3_list_already_not_in_crispr <- not_in_crispr_but_in_E3_list[!(not_in_crispr_but_in_E3_list %in% already_not_in_crispr)]

not_in_E3_list_already_not_in_crispr <- not_in_crispr_but_in_E3_list[!(not_in_E3_list_already_not_in_crispr %in% colnames(crispr)[3:length(colnames(crispr))])]

crispr_colnames <- toupper(colnames(crispr[3:length(colnames(crispr))]))
```


EGFR Mutant Lung

```{r mut_lung_crispr}
EGFRmutLung <- data.frame("cell_line_display_name" = c("NCIH1838", "ETCC016", "NCIH1573", "HCC827GR5", "NCAH3255", "HCC827", "NCAH1975", "HCC2935"), "lineage_1" = rep("Lung Mutant", 8))
crispr$lineage_1 <- ifelse(crispr$cell_line_display_name %in% EGFRmutLung$cell_line_display_name, "Lung Mutant", crispr$lineage_1)
```

Tally of Cancer types samples

```{r lineage_count_crispr}
rownames(crispr) <- crispr$cell_line_display_name
crispr$cell_line_display_name <- NULL
crispr_lineages_count <- crispr %>% group_by(lineage_1) %>% tally()
#crispr_lineages_count
#write.csv(x = crispr_lineages_count, file = paste0("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/E3_list/", Sys.Date(), "All_E3_lineage_count.csv"), row.names = FALSE)
```

**All_E3_lineage_count.csv** is generated here.


Only use Cancer types that have more than or equal to 5 samples. Update CRISPR dataframe 

```{r subset_CRISPR}
crispr_lineages_count <- filter(crispr_lineages_count, n >= 5) # greater than 5 samples
#crispr_lineages_count
crispr <- subset(crispr, lineage_1 %in% crispr_lineages_count$lineage_1)

```


Generating colors and breaks for lineages

```{r}
lineage_colors <- viridis(length(unique(crispr$lineage_1)))
lineage_breaks <- unique(crispr$lineage_1)
```


T-Test and Anova

```{r ttest and anova, eval =FALSE}
ttest_res <- data.frame(Lineage = lineage_breaks)
for(i in 2:ncol(crispr)) { # go through the 2nd col to the end
  genename <- colnames(crispr)[i] # saves the gene names in crispr
  df <- crispr[, c(1, i)] # df is a dataframe with all rows from crsipr and adding the gene and Chronos score
  colnames(df) <- c("Lineage", "Chronos") # label the cols
  # compare means performs one or multiple mean comparisons where Chronos is the numerical variable and
  # lineage is the group. ref.group='.all.' In this case, each of the grouping variable levels is compared to al
  ttest <- compare_means(Chronos ~ Lineage,  data = df, ref.group = ".all.", method = "t.test")
  # get p-adjusted value
  ttest <- ttest %>% dplyr::select(group2, p.adj)
  colnames(ttest) <- c("Lineage", genename) # change colnames
  ttest_res <- merge(ttest_res, ttest, by = "Lineage", all = TRUE)
  # use anova to compare means
  anova_res <- compare_means(Chronos ~ Lineage,  data = df, method = "anova", p.adjust.method = "BH")
  # Benjamini-Hochberg procedure, which is a method for controlling the false discovery rate (FDR) in multiple comparisons.
  plot <- ggplot(data = df, mapping = aes(x = reorder(Lineage, Chronos, median), y = Chronos)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(aes(color = Lineage), alpha = 0.6, width = 0.1) +
    stat_compare_means(label = "p.signif", method = "t.test", ref.group = ".all.", ) +
    labs(title = genename, subtitle = paste0("ANOVA, p-adj = ", anova_res$p.adj), y = "Chronos Dependency Score", "Lineage") +
    scale_color_manual(values = lineage_colors, breaks = lineage_breaks) +
    theme_linedraw() +
    theme(legend.position = "none", axis.text.x = element_text(angle = 90, hjust = 1))
  #draw(ht_crispr_pval)
  #ggsave(filename = paste0(Sys.Date(), "_", genename, "_DepMapChronos_byLineage.png"), path = "~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/", dpi = 300, device = "png", units = "in", height = 6, width = 10)
}
#write.csv(x = ttest_res, file = paste0("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/E3_list/", Sys.Date(), "_All_E3_ttest_res.csv"), row.names = FALSE)

```

**All_E3_ttest_res.csv** is generated here.




```{r, include=FALSE, eval =FALSE}
rownames(ttest_res) <- ttest_res$Lineage
ttest_res$Lineage <- NULL
require(circlize)
```



Heat map

```{r dist:method, eval =FALSE}
#dist: "euclidean", "maximum", "manhattan", "canberra", "binary", "minkowski", "pearson", "spearman", "kendall"

# Check for and remove constant values
ttest_res <- ttest_res[, apply(ttest_res, 2, function(x) length(unique(x)) > 1)]

# Remove rows/columns with missing values
ttest_res <- na.omit(ttest_res)

# Choose a different distance method
ht_crispr_pval <- Heatmap(
  matrix = as.matrix(ttest_res),
  name = "Adjusted p-value",
  #col = circlize::colorRamp2(c(0, 0.05, 0.05, 0.1, 0.5, 1), c("navy", "mediumblue", "white", "red", "darkred")),
  color_scale <- colorRamp2(breaks = c(0, 0.025, 0.05, 1), colors = c("navy", "mediumblue", "white", "white")),
#color_scale <- colorRamp2(breaks = c(0, 0.01, 0.02, 0.03, 0.04, 0.05), colors = c("navy", "mediumblue", "white", "white", "white")),
  row_title = "Lineage",
  row_split = rownames(ttest_res),
  column_title = NA,
  clustering_distance_rows = "pearson",
  clustering_distance_columns = "pearson",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_rows = TRUE,
  cluster_columns = TRUE,

heatmap_legend_param = list(legend_width = unit(3, "in"),
                                                      at = c(0, 0.01, 0.02, 0.03, 0.04, 0.05),
                                                      labels = c("0", "0.01", "0.02", "0.03", "0.04", "0.05"),
                                                      title_position = "topcenter",
                                                      legend_direction = "horizontal")
)

# Check for infinite or NaN values
if (any(is.infinite(as.matrix(ttest_res)) | is.nan(as.matrix(ttest_res)))) {
  stop("Data contains infinite or NaN values.")
}


png("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/Heatmaps/crispr_padj_heatmap_pearson_topcenter_v2.png", height = 8, width = 60, units = "in", res = 500)
draw(ht_crispr_pval, heatmap_legend_side = "top")
#ht_crispr_pval
dev.off()
```

**crispr_padj_heatmap_pearson.png** is generated here.









################################################################################


## sh/si RNA


```{r read_data_RNAi}
RNAi_achilles_demeter2 <- read.delim(file = "~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/sh:siRNA/RNAi_(Achilles,_DEMETER2)_subsetted.csv", header = TRUE, sep = ",", check.names = FALSE, stringsAsFactors = FALSE) # read in data
RNAi_achilles_drive <- read.delim(file = "~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/sh:siRNA/RNAi_(Achilles+DRIVE+Marcotte,_DEMETER2)_subsetted.csv", header = TRUE, sep = ",", check.names = FALSE, stringsAsFactors = FALSE) # read in data
RNAi_drive <- read.delim(file = "~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/sh:siRNA/RNAi_(DRIVE,_DEMETER2)_subsetted.csv", header = TRUE, sep = ",", check.names = FALSE, stringsAsFactors = FALSE) # read in data



RNAi_achilles_demeter2 <- RNAi_achilles_demeter2[, -c(1, 4, 5, 6, 7, 8)] # get rid of unneeded columns
RNAi_achilles_drive <- RNAi_achilles_drive[, -c(1, 4, 5, 6, 7, 8)] # get rid of unneeded columns
RNAi_drive <- RNAi_drive[, -c(1, 4, 5, 6, 7, 8)] # get rid of unneeded columns 

# get rid of missing data values
RNAi_achilles_demeter2 <- RNAi_achilles_demeter2[,!apply(is.na(RNAi_achilles_demeter2), 2, any)] # removes columns from the "RNAi_(Achilles,_DEMETER2)_subsetted" data that contain any missing values.
RNAi_achilles_drive <- RNAi_achilles_drive[,!apply(is.na(RNAi_achilles_drive), 2, any)] # removes columns from the "RNAi_(Achilles+DRIVE+Marcotte,_DEMETER2)_subsetted" data frame that contain any missing values.
RNAi_drive <- RNAi_drive[,!apply(is.na(RNAi_drive), 2, any)] # removes columns from the "RNAi_(DRIVE,_DEMETER2)_subsetted" data frame that contain any missing values.

```


EGFR Mutant Lung
This is not necessary to do since none of these genes should be in this RNAi data

```{r mut_lung_RNAi}
EGFRmutLung <- data.frame("cell_line_display_name" = c("NCIH1838", "ETCC016", "NCIH1573", "HCC827GR5", "NCAH3255", "HCC827", "NCAH1975", "HCC2935"), "lineage_1" = rep("Lung Mutant", 8))

RNAi_achilles_demeter2$lineage_1 <- ifelse(RNAi_achilles_demeter2$cell_line_display_name %in% EGFRmutLung$cell_line_display_name, "Lung Mutant", RNAi_achilles_demeter2$lineage_1)

RNAi_achilles_drive$lineage_1 <- ifelse(RNAi_achilles_drive$cell_line_display_name %in% EGFRmutLung$cell_line_display_name, "Lung Mutant", RNAi_achilles_drive$lineage_1)

RNAi_drive$lineage_1 <- ifelse(RNAi_drive$cell_line_display_name %in% EGFRmutLung$cell_line_display_name, "Lung Mutant", RNAi_drive$lineage_1)
```


Tally of Cancer types samples

```{r lineage_count_RNAi}
rownames(RNAi_achilles_demeter2) <- RNAi_achilles_demeter2$cell_line_display_name
RNAi_achilles_demeter2$cell_line_display_name <- NULL
RNAi_achilles_demeter2_lineages_count <- RNAi_achilles_demeter2 %>% group_by(lineage_1) %>% tally()

rownames(RNAi_achilles_drive) <- RNAi_achilles_drive$cell_line_display_name
RNAi_achilles_drive$cell_line_display_name <- NULL
RNAi_achilles_drive_lineages_count <- RNAi_achilles_drive %>% group_by(lineage_1) %>% tally()

rownames(RNAi_drive) <- RNAi_drive$cell_line_display_name
RNAi_drive$cell_line_display_name <- NULL
RNAi_drive_lineages_count <- RNAi_drive %>% group_by(lineage_1) %>% tally()


#RNAi_lineages_count save csv files
#write.csv(x = RNAi_achilles_demeter2_lineages_count, file = paste0("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/sh:siRNA/", Sys.Date(), "_RNAi_achilles_demeter2_lineages_count.csv"), row.names = FALSE)
#write.csv(x = RNAi_achilles_drive_lineages_count, file = paste0("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/sh:siRNA/", Sys.Date(), "_RNAi_achilles_drive_lineages_count.csv"), row.names = FALSE)
#write.csv(x = RNAi_drive_lineages_count, file = paste0("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/sh:siRNA/", Sys.Date(), "_RNAi_drive_lineages_count.csv"), row.names = FALSE)
```



Only use Cancer types that have more than or equal to 5 samples. Update RNAi dataframe 

```{r subset_RNAi}
RNAi_achilles_demeter2_lineages_count <- filter(RNAi_achilles_demeter2_lineages_count, n >= 5) # greater than 5 samples
RNAi_achilles_demeter2 <- subset(RNAi_achilles_demeter2, lineage_1 %in% RNAi_achilles_demeter2_lineages_count$lineage_1)


RNAi_achilles_drive_lineages_count <- filter(RNAi_achilles_drive_lineages_count, n >= 5) # greater than 5 samples
RNAi_achilles_drive <- subset(RNAi_achilles_drive, lineage_1 %in% RNAi_achilles_drive_lineages_count$lineage_1)


RNAi_drive_lineages_count <- filter(RNAi_drive_lineages_count, n >= 5) # greater than 5 samples
RNAi_drive <- subset(RNAi_drive, lineage_1 %in% RNAi_drive_lineages_count$lineage_1)

```




Generating colors and breaks for lineages

```{r}
lineage_colors <- viridis(length(unique(RNAi_achilles_demeter2$lineage_1)))
lineage_breaks <- unique(RNAi_achilles_demeter2$lineage_1)
```


```{r}
lineage_colors <- viridis(length(unique(RNAi_achilles_drive$lineage_1)))
lineage_breaks <- unique(RNAi_achilles_drive$lineage_1)
```


```{r}
lineage_colors <- viridis(length(unique(RNAi_drive$lineage_1)))
lineage_breaks <- unique(RNAi_drive$lineage_1)
```


## T-Test and Anova

RNAi_(Achilles+DRIVE+Marcotte,_DEMETER2)_subsetted
RNAi_achilles_demeter2

```{r ttest_and_anova_RNAi, eval =FALSE}
ttest_res_RNAi_achilles_demeter2 <- data.frame(Lineage = lineage_breaks)
for(i in 2:ncol(RNAi_achilles_demeter2)) { # go through the 2nd col to the end
  genename <- colnames(RNAi_achilles_demeter2)[i] # saves the gene names in crispr
  df_RNAi_achilles_demeter2 <- RNAi_achilles_demeter2[, c(1, i)] # df is a dataframe with all rows from crsipr and adding the gene and Chronos score
  colnames(df_RNAi_achilles_demeter2) <- c("Lineage", "Chronos") # label the cols
  # compare means performs one or multiple mean comparisons where Chronos is the numerical variable and
  # lineage is the group. ref.group='.all.' In this case, each of the grouping variable levels is compared to al
  ttest_RNAi_achilles_demeter2 <- compare_means(Chronos ~ Lineage,  data = df_RNAi_achilles_demeter2, ref.group = ".all.", method = "t.test")
  # get p-adjusted value
  ttest_RNAi_achilles_demeter2 <- ttest_RNAi_achilles_demeter2 %>% dplyr::select(group2, p.adj)
  colnames(ttest_RNAi_achilles_demeter2) <- c("Lineage", genename) # change colnames
  ttest_res_RNAi_achilles_demeter2 <- merge(ttest_res_RNAi_achilles_demeter2, ttest_RNAi_achilles_demeter2, by = "Lineage", all = TRUE)
  # use anova to compare means
  anova_res_RNAi_achilles_demeter <- compare_means(Chronos ~ Lineage,  data = df_RNAi_achilles_demeter2, method = "anova", p.adjust.method = "BH")
  # Benjamini-Hochberg procedure, which is a method for controlling the false discovery rate (FDR) in multiple comparisons.
  plot <- ggplot(data = df_RNAi_achilles_demeter2, mapping = aes(x = reorder(Lineage, Chronos, median), y = Chronos)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(aes(color = Lineage), alpha = 0.6, width = 0.1) +
    stat_compare_means(label = "p.signif", method = "t.test", ref.group = ".all.", ) +
    labs(title = genename, subtitle = paste0("ANOVA, p-adj = ", anova_res_RNAi_achilles_demeter$p.adj), y = "Chronos Dependency Score", "Lineage") +
    scale_color_manual(values = lineage_colors, breaks = lineage_breaks) +
    theme_linedraw() +
    theme(legend.position = "none", axis.text.x = element_text(angle = 90, hjust = 1))
  #draw(ht_crispr_pval)
  #ggsave(filename = paste0(Sys.Date(), "_", genename, "_DepMapChronos_byLineage.png"), path = "~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/", dpi = 300, device = "png", units = "in", height = 6, width = 10)
}
write.csv(x = ttest_res_RNAi_achilles_demeter2, file = paste0("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/sh:siRNA/", Sys.Date(), "_ttest_res_RNAi_achilles_demeter2.csv"), row.names = FALSE)

```





```{r, eval =FALSE}
rownames(ttest_res_RNAi_achilles_demeter2) <- ttest_res_RNAi_achilles_demeter2$Lineage
ttest_res_RNAi_achilles_demeter2$Lineage <- NULL
require(circlize)
```



Heat map

```{r dist:method_RNAi, eval =FALSE}
#dist: "euclidean", "maximum", "manhattan", "canberra", "binary", "minkowski", "pearson", "spearman", "kendall"

# Check for and remove constant values
ttest_res_RNAi_achilles_demeter2 <- ttest_res_RNAi_achilles_demeter2[, apply(ttest_res_RNAi_achilles_demeter2, 2, function(x) length(unique(x)) > 1)]

# Remove rows/columns with missing values
ttest_res_RNAi_achilles_demeter2 <- na.omit(ttest_res_RNAi_achilles_demeter2)

# Choose a different distance method
ht_RNAi_pval <- Heatmap(
  matrix = as.matrix(ttest_res_RNAi_achilles_demeter2),
  name = "Adjusted p-value",
  #col = circlize::colorRamp2(c(0, 0.05, 0.05, 0.1, 0.5, 1), c("navy", "mediumblue", "white", "red", "darkred")),
  color_scale <- colorRamp2(breaks = c(0, 0.025, 0.05, 1), colors = c("navy", "mediumblue", "white", "white")),
#color_scale <- colorRamp2(breaks = c(0, 0.01, 0.02, 0.03, 0.04, 0.05), colors = c("navy", "mediumblue", "white", "white", "white")),
  row_title = "Lineage",
  row_split = rownames(ttest_res_RNAi_achilles_demeter2),
  column_title = NA,
  clustering_distance_rows = "pearson",
  clustering_distance_columns = "pearson",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_rows = TRUE,
  cluster_columns = TRUE,

heatmap_legend_param = list(legend_width = unit(3, "in"),
                                                      at = c(0, 0.01, 0.02, 0.03, 0.04, 0.05),
                                                      labels = c("0", "0.01", "0.02", "0.03", "0.04", "0.05"),
                                                      title_position = "topcenter",
                                                      legend_direction = "horizontal")
)

# Check for infinite or NaN values
if (any(is.infinite(as.matrix(ttest_res_RNAi_achilles_demeter2)) | is.nan(as.matrix(ttest_res_RNAi_achilles_demeter2)))) {
  stop("Data contains infinite or NaN values.")
}


png("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/Heatmaps/RNAi_heatmap_RNAi_(Achilles,_DEMETER2).png", height = 8, width = 60, units = "in", res = 500)
draw(ht_RNAi_pval, heatmap_legend_side = "top")
#ht_RNAi_pval
dev.off()
```









RNAi_(Achilles+DRIVE+Marcotte,_DEMETER2)_subsetted
RNAi_achilles_drive

```{r ttest_and_anova_RNAi_drive, eval =FALSE}
ttest_res_RNAi_achilles_drive <- data.frame(Lineage = lineage_breaks)
for(i in 2:ncol(RNAi_achilles_drive)) { # go through the 2nd col to the end
  genename <- colnames(RNAi_achilles_drive)[i] # saves the gene names in crispr
  df_RNAi_achilles_drive <- RNAi_achilles_drive[, c(1, i)] # df is a dataframe with all rows from RNAi_achilles_drive and adding the gene and Chronos score
  colnames(df_RNAi_achilles_drive) <- c("Lineage", "Chronos") # label the cols
  # compare means performs one or multiple mean comparisons where Chronos is the numerical variable and
  # lineage is the group. ref.group='.all.' In this case, each of the grouping variable levels is compared to al
  ttest_RNAi_achilles_drive <- compare_means(Chronos ~ Lineage,  data = df_RNAi_achilles_drive, ref.group = ".all.", method = "t.test")
  # get p-adjusted value
  ttest_RNAi_achilles_drive <- ttest_RNAi_achilles_drive %>% dplyr::select(group2, p.adj)
  colnames(ttest_RNAi_achilles_drive) <- c("Lineage", genename) # change colnames
  ttest_res_RNAi_achilles_drive <- merge(ttest_res_RNAi_achilles_drive, ttest_RNAi_achilles_drive, by = "Lineage", all = TRUE)
  # use anova to compare means
  anova_res_RNAi_achilles_drive <- compare_means(Chronos ~ Lineage,  data = df_RNAi_achilles_drive, method = "anova", p.adjust.method = "BH")
  # Benjamini-Hochberg procedure, which is a method for controlling the false discovery rate (FDR) in multiple comparisons.
  plot <- ggplot(data = df_RNAi_achilles_drive, mapping = aes(x = reorder(Lineage, Chronos, median), y = Chronos)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(aes(color = Lineage), alpha = 0.6, width = 0.1) +
    stat_compare_means(label = "p.signif", method = "t.test", ref.group = ".all.", ) +
    labs(title = genename, subtitle = paste0("ANOVA, p-adj = ", anova_res_RNAi_achilles_drive$p.adj), y = "Chronos Dependency Score", "Lineage") +
    scale_color_manual(values = lineage_colors, breaks = lineage_breaks) +
    theme_linedraw() +
    theme(legend.position = "none", axis.text.x = element_text(angle = 90, hjust = 1))
  #draw(ht_crispr_pval)
  #ggsave(filename = paste0(Sys.Date(), "_", genename, "_DepMapChronos_byLineage.png"), path = "~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/", dpi = 300, device = "png", units = "in", height = 6, width = 10)
}
#write.csv(x = ttest_res_RNAi_achilles_drive, file = paste0("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/sh:siRNA/", Sys.Date(), "_ttest_res_RNAi_achilles_drive.csv"), row.names = FALSE)

```





```{r, eval =FALSE}
rownames(ttest_res_RNAi_achilles_drive) <- ttest_res_RNAi_achilles_drive$Lineage
ttest_res_RNAi_achilles_drive$Lineage <- NULL
require(circlize)
```



Heat map

```{r dist:method_RNAi_drive, eval =FALSE}
#dist: "euclidean", "maximum", "manhattan", "canberra", "binary", "minkowski", "pearson", "spearman", "kendall"

# Check for and remove constant values
ttest_res_RNAi_achilles_drive <- ttest_res_RNAi_achilles_drive[, apply(ttest_res_RNAi_achilles_drive, 2, function(x) length(unique(x)) > 1)]

# Remove rows/columns with missing values
ttest_res_RNAi_achilles_drive <- na.omit(ttest_res_RNAi_achilles_drive)

# Choose a different distance method
ht_RNAi_pval <- Heatmap(
  matrix = as.matrix(ttest_res_RNAi_achilles_drive),
  name = "Adjusted p-value",
  #col = circlize::colorRamp2(c(0, 0.05, 0.05, 0.1, 0.5, 1), c("navy", "mediumblue", "white", "red", "darkred")),
  color_scale <- colorRamp2(breaks = c(0, 0.025, 0.05, 1), colors = c("navy", "mediumblue", "white", "white")),
#color_scale <- colorRamp2(breaks = c(0, 0.01, 0.02, 0.03, 0.04, 0.05), colors = c("navy", "mediumblue", "white", "white", "white")),
  row_title = "Lineage",
  row_split = rownames(ttest_res_RNAi_achilles_drive),
  column_title = NA,
  clustering_distance_rows = "pearson",
  clustering_distance_columns = "pearson",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_rows = TRUE,
  cluster_columns = TRUE,

heatmap_legend_param = list(legend_width = unit(3, "in"),
                                                      at = c(0, 0.01, 0.02, 0.03, 0.04, 0.05),
                                                      labels = c("0", "0.01", "0.02", "0.03", "0.04", "0.05"),
                                                      title_position = "topcenter",
                                                      legend_direction = "horizontal")
)

# Check for infinite or NaN values
if (any(is.infinite(as.matrix(ttest_res_RNAi_achilles_drive)) | is.nan(as.matrix(ttest_res_RNAi_achilles_drive)))) {
  stop("Data contains infinite or NaN values.")
}


png("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/Heatmaps/RNAi_(Achilles+DRIVE+Marcotte,_DEMETER2).png", height = 8, width = 60, units = "in", res = 500)
draw(ht_RNAi_pval, heatmap_legend_side = "top")
#ht_RNAi_pval
dev.off()
```








RNAi_(DRIVE,_DEMETER2)_subsetted
RNAi_drive

```{r ttest_and_anova_RNAi_dem2, eval =FALSE}
ttest_res_RNAi_drive <- data.frame(Lineage = lineage_breaks)
for(i in 2:ncol(RNAi_drive)) { # go through the 2nd col to the end
  genename <- colnames(RNAi_drive)[i] # saves the gene names in crispr
  df_RNAi_drive <- RNAi_drive[, c(1, i)] # df is a dataframe with all rows from RNAi_drive and adding the gene and Chronos score
  colnames(df_RNAi_drive) <- c("Lineage", "Chronos") # label the cols
  # compare means performs one or multiple mean comparisons where Chronos is the numerical variable and
  # lineage is the group. ref.group='.all.' In this case, each of the grouping variable levels is compared to al
  ttest_RNAi_drive <- compare_means(Chronos ~ Lineage,  data = df_RNAi_drive, ref.group = ".all.", method = "t.test")
  # get p-adjusted value
  ttest_RNAi_drive <- ttest_RNAi_drive %>% dplyr::select(group2, p.adj)
  colnames(ttest_RNAi_drive) <- c("Lineage", genename) # change colnames
  ttest_res_RNAi_drive <- merge(ttest_res_RNAi_drive, ttest_RNAi_drive, by = "Lineage", all = TRUE)
  # use anova to compare means
  anova_res_RNAi_drive <- compare_means(Chronos ~ Lineage,  data = df_RNAi_drive, method = "anova", p.adjust.method = "BH")
  # Benjamini-Hochberg procedure, which is a method for controlling the false discovery rate (FDR) in multiple comparisons.
  plot <- ggplot(data = df_RNAi_drive, mapping = aes(x = reorder(Lineage, Chronos, median), y = Chronos)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(aes(color = Lineage), alpha = 0.6, width = 0.1) +
    stat_compare_means(label = "p.signif", method = "t.test", ref.group = ".all.", ) +
    labs(title = genename, subtitle = paste0("ANOVA, p-adj = ", anova_res_RNAi_drive$p.adj), y = "Chronos Dependency Score", "Lineage") +
    scale_color_manual(values = lineage_colors, breaks = lineage_breaks) +
    theme_linedraw() +
    theme(legend.position = "none", axis.text.x = element_text(angle = 90, hjust = 1))
  #draw(ht_crispr_pval)
  #ggsave(filename = paste0(Sys.Date(), "_", genename, "_DepMapChronos_byLineage.png"), path = "~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/", dpi = 300, device = "png", units = "in", height = 6, width = 10)
}
write.csv(x = ttest_res_RNAi_drive, file = paste0("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/sh:siRNA/", Sys.Date(), "_ttest_res_RNAi_drive.csv"), row.names = FALSE)

```





```{r, eval =FALSE}
rownames(ttest_res_RNAi_drive) <- ttest_res_RNAi_drive$Lineage
ttest_res_RNAi_drive$Lineage <- NULL
require(circlize)
```



Heat map

```{r dist:method_RNAi_dem2, eval =FALSE}
#dist: "euclidean", "maximum", "manhattan", "canberra", "binary", "minkowski", "pearson", "spearman", "kendall"

# Check for and remove constant values
ttest_res_RNAi_drive <- ttest_res_RNAi_drive[, apply(ttest_res_RNAi_drive, 2, function(x) length(unique(x)) > 1)]

# Remove rows/columns with missing values
ttest_res_RNAi_drive <- na.omit(ttest_res_RNAi_drive)

# Choose a different distance method
ht_RNAi_pval <- Heatmap(
  matrix = as.matrix(ttest_res_RNAi_drive),
  name = "Adjusted p-value",
  #col = circlize::colorRamp2(c(0, 0.05, 0.05, 0.1, 0.5, 1), c("navy", "mediumblue", "white", "red", "darkred")),
  color_scale <- colorRamp2(breaks = c(0, 0.025, 0.05, 1), colors = c("navy", "mediumblue", "white", "white")),
#color_scale <- colorRamp2(breaks = c(0, 0.01, 0.02, 0.03, 0.04, 0.05), colors = c("navy", "mediumblue", "white", "white", "white")),
  row_title = "Lineage",
  row_split = rownames(ttest_res_RNAi_drive),
  column_title = NA,
  clustering_distance_rows = "pearson",
  clustering_distance_columns = "pearson",
  show_row_dend = FALSE,
  show_column_dend = FALSE,
  cluster_rows = TRUE,
  cluster_columns = TRUE,

heatmap_legend_param = list(legend_width = unit(3, "in"),
                                                      at = c(0, 0.01, 0.02, 0.03, 0.04, 0.05),
                                                      labels = c("0", "0.01", "0.02", "0.03", "0.04", "0.05"),
                                                      title_position = "topcenter",
                                                      legend_direction = "horizontal")
)

# Check for infinite or NaN values
if (any(is.infinite(as.matrix(ttest_res_RNAi_drive)) | is.nan(as.matrix(ttest_res_RNAi_drive)))) {
  stop("Data contains infinite or NaN values.")
}


png("~/Desktop/Weill_Cornell_Graduate/Grad_School/Thesis/Heatmaps/RNAi_(DRIVE,_DEMETER2).png", height = 8, width = 60, units = "in", res = 500)
draw(ht_RNAi_pval, heatmap_legend_side = "top")
#ht_RNAi_pval
dev.off()
```









